Authors Response to Reviewer Comments

### 2023-09-19 manuscript/manuscriptRW.Rmd
added basic structure for review
review documents and updates on the original manuscript
comments 5-7 reviewer 2

    reference_docx: template_paper.docxl

@@

**OPEN RESEARCH STATEMENT:** This submission uses novel code, both the data
and code are provided in an external repository to be evaluated during
the peer review process. The repository can be downloaded from
[this figshare private link: https://figshare.com/s/100857ba67d2351dcb15](https://figshare.com/s/100857ba67d2351dcb15). The protocol is available at @díaz-yáñez2022 ([with link: https://osf.io/czdxp/](https://osf.io/czdxp/ )). We
will make publicly available the code and data if the manuscript is accepted.

@@

Tree regeneration is a key process in forest dynamics, particularly in
the context of forest resilience and climate change. Models are pivotal
for assessing long-term forest dynamics, and they have been in use for
more than 50 years. However, an assessment of their ability to
accurately represent tree regeneration is lacking. We assess how well
current models capture the overall abundance, species composition, and
mortality of tree regeneration.

Using 15 models built to capture long-term forest dynamics at the stand,
landscape, and global levels, we simulate tree regeneration at 200 sites
representing large environmental gradients across Central Europe. The
results are evaluated against comprehensive data from unmanaged forests.

Most of the models overestimate regeneration levels, which is only
compensated in some models by high simulated mortality rates in the
early stages of individual trees dynamics. Simulated species diversity
of regeneration matches the observed ranges. Models simulating higher
species diversity at the stand level do not feature higher regeneration
diversity. The effect of light availability on regeneration levels is
captured better than the effect of temperature and soil moisture, but
patterns are not consistent across models. Increasing complexity in the
tree regeneration modules of the models is not related to higher
accuracy of simulated tree regeneration. Furthermore, individual model
design is more important than scale (stand, landscape, global) and
approach (empirical, process-based) for accurately capturing tree
regeneration.

>>>>

    reference_docx: template_paper.docx

@@

**OPEN RESEARCH STATEMENT:** This submission uses novel code, both the
data and code are provided in an external repository to be evaluated
during the peer review process. The repository can be downloaded from
[this figshare private link:
https://figshare.com/s/100857ba67d2351dcb15](https://figshare.com/s/100857ba67d2351dcb15).
The protocol is available at @díaz-yáñez2022 ([with link:
https://osf.io/czdxp/](https://osf.io/czdxp/)). We will make publicly
available the code and data if the manuscript is accepted.

@@

Tree regeneration is a key process in forest dynamics, particularly in
the context of forest resilience and climate change. Models are pivotal
for assessing long-term forest dynamics, and they have been in use for
more than 50 years. However, there is a need to evaluate their capacity
to accurately represent tree regeneration. We assess how well current
models capture the overall abundance, species composition, and mortality
of tree regeneration.

Using 15 models built to capture long-term forest dynamics at the stand,
landscape, and global levels, we simulate tree regeneration at 200 sites
representing large environmental gradients across Central Europe. The
results are evaluated against extensive data from unmanaged forests.

Most of the models overestimate regeneration levels, which is only
compensated in some models by high simulated mortality rates in the
early stages of individual trees dynamics. Simulated species diversity
of regeneration matches the observed ranges. Models simulating higher
species diversity at the stand level do not present higher regeneration
diversity. The effect of light availability on regeneration levels is
captured better than the effect of temperature and soil moisture, but
patterns are not consistent across models. Increasing complexity in the
tree regeneration modules of the models is not related to higher
accuracy of simulated tree regeneration. Furthermore, individual model
design is more important than scale (stand, landscape, global) and
approach (empirical, process-based) for accurately capturing tree
regeneration.

### 2023-09-19 manuscript/review/authorsResponse.qmd
comments 5-7 reviewer 2

These comment have been extracted from the reviewer 2 comments on the PDF document of the manuscript.

@@

@@

@@

>>>>

These comments have been extracted from the reviewer 2 comments on the PDF document of the manuscript.

@@

Based on the reviewers comments we have modified this sentence to: "However, there is a need to evaluate their capacity to accurately represent tree regeneration"

@@

Following the reviewers comment we have changed the word "comprehensive" to "extensive" to express that we used a wide-range data that considers many important elements of regeneration.

@@

Following the reviewers comments we have changed "feature" with "present".
